---
title: "Get started"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

As usual, start by using the r2dii package with:

```{r}
library(r2dii)
```

## Creating data snapshots

`take_snapshot()` allows you to take snapshots of multiple datasets. Its default behavior is sensible, but conservative and potentially slow (see `take_snapshot()`). You may want to change the default arguments.

Use:

* `datasets` to snapshot specific datasets.
* Use `destdir` to customize the destination directory.
* Use `config` to provide a custom configuration file to `take_snapshot()`.

```{r}
datasets <- c("RevenueSplit", "BENCH.REGIONS")
custom_destdir <- tempdir()
custom_config <- example_config("config-toy.yml")

take_snapshot(
  datasets,
  destdir = custom_destdir, 
  config = custom_config
)
```

Use:

* `overwrite = TRUE` to overwrite existing snapshots.

```{r}
take_snapshot(
  datasets,
  destdir = custom_destdir, 
  config = custom_config
)

# Overwrite
take_snapshot(
  datasets,
  destdir = custom_destdir, 
  config = custom_config,
  overwrite = TRUE
)
```

* `options(r2dii_config = <custom_config>)` replaces `config` and affects your R session globally.

```{r}
restore <- options(r2dii_config = custom_config)

take_snapshot(
  datasets,
  destdir = custom_destdir, 
  overwrite = TRUE
)

options(restore)
```

## Documentation

You can access the high level documentation of the package with `?r2dii.dataraw`. At the bottom you may click _Index_ to access the help files of all topics. As usual, you can access the help file of any topic with `?topic`.

A good way to learn about discover useful features is to run a [Global search](https://2degreesinvesting.github.io/r2dii/articles/reference.html#global-search) using a keyword, or to navigate the table of [Contents](https://2degreesinvesting.github.io/r2dii/articles/reference.html#tocnav). In any case, click on the question mark next to the name of any feature to access its documentation.

## Create paths

A family of functions create robust paths.

```{r}
path_dropbox_2dii()
```

(For you, the root directory might be similar to `C:/Users/You/...`)

## Configuration file

A family of functions help you to deal with the configuration file.

`edit_config()` opens the default configuration file so you can edit it.

```r
if (interactive()) edit_config()
```

(I'm not in an interactive session so the chunk above won't run.)

`get_config()` outputs a path to a configuration file. By default it outputs the path to a toy configuration file with a warning.

```{r}
default_config <- get_config()
```

`show_config()` shows a configuration file.

```{r, comment=""}
show_config(default_config, n_max = 5)
```

Most analyses should start by setting a custom configuration file globally with `options()`.

```{r, comment=""}
your_config <- example_config("config-toy.yml")
restore <- options(r2dii_config = your_config)

get_config()

show_config(get_config())

options(restore)
```

## Access configuration parameters and create configuration-sensitive paths

A family of functions are sensitive to the configuration file you use. This includes all functions to access configuration parameters, and some of the functions to create paths.

```{r}
a_config <- example_config("config_2019Q2.yml")
restore <- options(r2dii_config = a_config)

FINANCIAL.TIMESTAMP()

another_config <- example_config("config-toy.yml")
options(r2dii_config = another_config)

FINANCIAL.TIMESTAMP()

options(restore)
```

## Extending functions to access configuration parameters

Eventually you will likely need to access new configuration parameters. How would you expand this family of functions?

To show you how let me first create a mini configuration file and save it to a temporary directory.

```{r, comment=""}
# Create an example configuration file
config <- glue::glue("
   default:
     a_field: a_value
 ")

show_config(config)

# Write the config file to a temporary file
config_file <- tempfile()
readr::write_lines(config, config_file)
```

Use `get_param()` to create new functions to access configuration parameters. Here, for example, `get_a_value()` gets `a_value` from `a_field`:

```{r}
get_a_value <- get_param("a_field")
get_a_value(file = config_file)
```

## Datasets

A family of functions allow you to read local datasets from your local 2dii Dropbox-folder, e.g.:

```{r}
INDEX.REGIONS()

GROUPS.GOVT()
```

Remember that the datasets you get may be sensitive to the configuration file. If in doubt, check which file are you using with `get_config()`.
