---
title: "Get started"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

As usual, start by using the r2dii package with:

```{r}
library(r2dii)
```

## Creating data snapshots

```{r, child="take-snapshot.Rmd"}

```

## Documentation

You can access the high level documentation of the package with `?r2dii.dataraw`. At the bottom you may click _Index_ to access the help files of all topics. As usual, you can access the help file of any topic with `?topic`.

A good way to learn about all features is to explore the "r2dii.dataraw" tab of the private package-website:

```r
if (interactive()) browse_private_site()
```

Please help me improve the documentation via pull requests.

## Create paths

A family of functions create robust paths.

```{r}
path_dropbox_2dii()
```

For this to work, you must have the Dropbox folder of 2dii directly under home (the default location).

```{r}
fs::dir_ls(fs::path_home(), regexp = "Dropbox")
```

## Configuration file

A family of functions help you to deal with the configuration file.

`edit_config()` opens the default configuration file so you can edit it.

```r
if (interactive()) edit_config()
```

(I'm not in an interactive session so the chunk above won't run.)

`get_config()` outputs a path to a configuration file. By default it outputs the  path to the default configuration file -- stored in the r2dii.dataraw package.

```{r}
get_config()
```

`show_config()` shows a configuration file.

```{r, comment=""}
show_config(get_config(), n_max = 10)
```

You can change the default configuration file globally via `options()`.

```{r, comment=""}
your_config <- example_config("config-toy.yml")
restore <- options(r2dii_config = your_config)

get_config()

show_config(get_config())

options(restore)
```

## Access configuration parameters and create configuration-sensitive paths

A family of functions are sensitive to the configuration file you use. This includes all functions to access configuration parameters, and some of the functions to create paths.

```{r}
# Using the default configuration file
getOption("r2dii_config")
FINANCIAL.TIMESTAMP()
FIN.DATA.PATH()

# Using your configuration file
your_config <- example_config("config-toy.yml")
restore <- options(r2dii_config = your_config)
FINANCIAL.TIMESTAMP()
FIN.DATA.PATH()

options(restore)
```

## Extending functions to access configuration parameters

Eventually you will likely need to access new configuration parameters. How would you expand this family of functions?

Use `get_param()` to create new functions to access configuration parameters.

```{r, comment=""}
# Create a `get_a_value()` function to get `a_value` from `a_field`
get_a_value <- get_param("a_field")

# Create an example configuration file
config <- glue::glue("
   default:
     a_field: a_value
 ")

show_config(config)
```

```{r}
# Write the config file to a temporary file
config_file <- tempfile()
readr::write_lines(config, config_file)

get_a_value(file = config_file)
```

## Datasets

A family of functions allow you to read local datasets from your local 2dii Dropbox-folder, e.g.:

```r
# Not showing this for privacy
ALD.BV()
```

A family of datasets become directly available when you attach the r2dii.dataraw package, e.g.:

```{r}
INDEX.REGIONS

GROUPS.GOVT
```

Some datasets are sensitive to the configuration file, which you can always check with `get_config()`.

```{r}
get_config()
```

