```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>"
)

library(dplyr)
library(pkgdoc)
library(r2dii)
```

```{r, warning=FALSE}
url_r2dii <- "https://2degreesinvesting.github.io/"
search_default <- "dataset"

r2dii_reference_concept <- function(x) {
  reference_concept(x, url = url_r2dii, packages = r2dii_packages()) %>% 
    custom_table()
}
r2dii_reference_package <- function(x) {
  reference_package(x, url = url_r2dii, packages = r2dii_packages()) %>% 
    custom_table()
}
custom_table <- function(x) {
  x %>% 
    select(-package, -concept) %>% 
    unique() %>%
    knitr::kable(
      x, 
      format = "html",
      col.names = NULL,
      escape = FALSE
    ) %>%
    kableExtra::column_spec(1, bold = TRUE) %>% 
    kableExtra::column_spec(2, width = "20em")
}
```

Search globally in the search box below, or navigate the index clicking the menu on the right.

### Global search

```{r global-search, warning=FALSE}
r2dii_packages() %>% 
  purrr::map_dfr(reference_package, url = url_r2dii) %>% 
  select(-package, -concept) %>% 
  unique() %>% 
  purrr::set_names(c("", "object", "description")) %>% 
  DT::datatable(
    escape = FALSE,
    rownames = NULL,
    options = list(
      # f: filter, t: table, i: information
      dom = "fti",
      search = list(search = search_default)
    )
  )
```

### Handle dataset snapshots

```{r}
r2dii_reference_concept("handle snapshots")
```

### Handle the configuration file

```{r}
r2dii_reference_concept("functions to deal with configuration files")
```

### Documentation for generic datasets

```{r}
r2dii_reference_concept("generic datasets")
```

### Exported datasets

These datasets are directly accessible when you attach the package.

```{r}
r2dii_reference_concept("demo datasets")
```

### Datasets in Reference

These datasets are accessible via functions that get them from a local copy of 2dii's Dropbox folder.

```{r}
r2dii_reference_concept("datasets in Reference")
r2dii_reference_concept("datasets in Reference to remove or outsource to data store")
```

### Datastore datasets

These datasets are accessible via functions that get them from a local copy of 2dii's Dropbox folder.

```{r}
r2dii_reference_concept("datasets in datastore")
```

### Other datasets

These datasets are accessible via functions that get them from a local copy of 2dii's Dropbox folder.

```{r}
r2dii_reference_concept("datasets in directories other than Reference or datastore")
```

### Paths pointing to 2dii's dropbox-folder

These datasets are accessible via functions that get them from a local copy of 2dii's Dropbox folder.

```{r}
r2dii_reference_concept("functions to output paths depending on a configuration file")
r2dii_reference_concept("functions to output 2dii paths")
```

### Access configuration parameters

```{r}
r2dii_reference_concept("functions to get specific 2dii configuration parameters")
```

### Miscellaneous

```{r}
r2dii_reference_concept("miscellaneous utility functions")
```
