```{r, include=FALSE}
library(r2dii)
```

`take_snapshot()` allows you to take snapshots of multiple datasets. Its default behavior is sensible, but conservative and potentially slow (see `take_snapshot()`). You may want to change the default arguments.

Use:

* `datasets` to snapshot specific datasets.
* Use `destdir` to customize the destination directory.
* Use `config` to provide a custom configuration file to `take_snapshot()`.

```{r}
datasets <- c("RevenueSplit", "EQMarket.Size")
custom_destdir <- tempdir()
custom_config <- example_config("config-toy.yml")

take_snapshot(
  datasets,
  destdir = custom_destdir, 
  config = custom_config
)
```

Use:

* `overwrite = TRUE` to overwrite existing snapshots.

```{r}
take_snapshot(
  datasets,
  destdir = custom_destdir, 
  config = custom_config
)

# Overwrite
take_snapshot(
  datasets,
  destdir = custom_destdir, 
  config = custom_config,
  overwrite = TRUE
)
```

* `options(r2dii_config = <custom_config>)` replaces `config` and affects your R session globally.

```{r}
restore <- options(r2dii_config = custom_config)

take_snapshot(
  datasets,
  destdir = custom_destdir, 
  overwrite = TRUE
)

options(restore)
```
